\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-17 NAR_DRAFT.tex
add text to describe the mutation profile figure in more detail

The mutational processes that generate single nucleotide variants in tumors do not act uniformly across the genome.
%Single nucleotide variants arise in tumors at a rate and at genomic locations driven by two main processes. 
The processes of spontaneous mutation that are active in all somatic tissues depend sensitively on local nucleotide context \citep{Nik-Zainal2012a,Alexandrov2015,Lee-Six2018}. 
Additional mutational processes are active in tumors, due to mutagen exposure or defects in DNA maintenance and repair, and these processes are also sensitive to local nucleotide context \citep{Alexandrov2013a,Helleday2014a,Nik-Zainal2016,Kandoth2013,Alexandrov2016}.
The specific mutational processes active in a particular tumor generate its unique mutation profile, and differences within and between tumor types are pronounced \cite{Stephens2005, Burrell2013a, Nakamura2015, Witkiewicz2015, Kumar2016}.
For example, Figure \ref{NAR-sigfig}\textbf{A}--\textbf{C}, shows mutation profiles from several tumors.
\rngcomment{Check how NAR Genomics and Bioinformatics formats figure legends, equation references, etc.}
\bkmcomment{Fixed in portions of text. need to change all figures to have capital letter panel labels. A and so on.}
%Figure \ref{NAR-sigfig} \textbf{a-e} shows several examples of mutation profiles from both real and simulated tumors.

>>>>

The mutational processes that generate single nucleotide variants in tumors do not act uniformly across the genome.
%Single nucleotide variants arise in tumors at a rate and at genomic locations driven by two main processes. 
The processes of spontaneous mutation that are active in all somatic tissues depend sensitively on local nucleotide context \citep{Nik-Zainal2012a,Alexandrov2015,Lee-Six2018}. 
Additional mutational processes are active in tumors, due to mutagen exposure or defects in DNA maintenance and repair, and these processes are also sensitive to local nucleotide context \citep{Alexandrov2013a,Helleday2014a,Nik-Zainal2016,Kandoth2013,Alexandrov2016}.
The specific mutational processes active in a particular tumor generate its unique mutation profile, and differences within and between tumor types are pronounced \cite{Stephens2005, Burrell2013a, Nakamura2015, Witkiewicz2015, Kumar2016}.
For example, Figure~\ref{NAR-sigfig}, shows mutation profiles from several tumors.
These real tumor mutation profiles show the diversity of profiles seen even within a single cancer.
The synthetic tumor mutation profiles we generated are designed to capture this diversity, and assess the performance of \batcave across a spectrum of reasonable mutation profiles.
%Figure \ref{NAR-sigfig} \textbf{a-e} shows several examples of mutation profiles from both real and simulated tumors.
